\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-06-11 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

To check the robustness of the result, we calculate the HHI index for each segmented market which is defined as $HHI = \sum_{i=1}^N (s_i)^2$ where $s_i$ is the market share of firm $i$ expressed as a percentage. Then we estimate the model by separating the samples to those with high HHI and low HHI where HHI is greater than 2000 and less than 2000. The results are shown in Table \ref{tab:sylized_fact_hetero_hhi}. The result indicates that

Moreover, to check the heterogeneity issue, we also classifies the we also report the results of the robustness check of the dynamic model. The results show that the dynamic model Table \ref{tab:sylized_fact_hetero_mature}

@@

In the preceding section, our research has been directed toward evaluating the dynamic effect of Lianjia's offline stores operation. However, there is an imperative to conduct a more detailed analysis of the impact of Lianjia's entry on regional transaction properties. The core of this necessary analysis derives from the premise that the entry of a Lianjia represents an exogenous shock within the respective local segmented market, thus providing a unique opportunity to study the effect of offline expansion on local real estate market. To facilitate such an analysis, we have constructed a series of dummy variables associated with the presence of the Lianjia within the marketplace, delineated as $pre_2$, $pre_1$ (before entry), $entry$, $post_1$, $post_2$, and $post_3$ (successive post-entry intervals), which encapsulate the respective temporal epochs relative to the Lianjia's entry. These binary indicators serve as central regressors within a structured econometric model with $pre_1$ as the control group, described in Equation \eqref{eq:entry_effect}:

@@

In the post-entry periods ($post_1$, $post_2$, and $post_3$), the results vary. The first period after entry ($post_1$) shows no significant changes in any of the results. However, after two post-entry periods ($post_2$ and $post_3$), there are significant negative effects on both revenue and number of house tours. These declines suggest a decline in the performance and engagement of the Lianjia, possibly due to the impact of an epidemic that led to a decrease in revenue and showing

@@

To check the robustness of the entry effect, we also conduct the

@@

We treat the year 2016 as the base year, and other settings are consistent with previous table \ref{tab:Dynamic}. The result is reported in Figure \ref{fig:dynamic_effect}

@@

@@

>>>>

To verify the robustness of our results, we calculated the Herfindahl-Hirschman Index (HHI) for each segmented market, defined as $HHI = \sum_{i=1}^N (s_i)^2$ where $s_i$ is the market share of firm $i$ expressed as a percentage. We then estimated the model by dividing the sample into high HHI (greater than 2000) and low HHI (less than 2000) groups. The results, shown in Table \ref{tab:sylized_fact_hetero_hhi}, indicate that Lianjia's offline stores have a more substantial impact on transaction properties in more competitive markets compared to more monopolized ones. This effect arises from two main factors: first, Lianjia's market power is insufficient to exclude other competitors from entering the market, and second, the area may not be attractive to other competitors, resulting in a larger market share for Lianjia. Furthermore, to address the heterogeneity issue, we introduced a dummy variable equal to one if the market already had Lianjia presence before 2016 and estimated the model by separating the sample based on this criterion. The results, presented in Table \ref{tab:sylized_fact_hetero_mature}, demonstrate that the years 2017, 2018, and 2019 have a significant positive impact on Lianjia's revenue in this segmented market. Another interesting phenomenon observed is that the number of house tours is significant for the years 2018 and 2019 in the lower maturity group, whereas in the higher maturity group, the number of house tours becomes significant in 2020. These findings indicate that in less mature markets, the entry of Lianjia drives increased profitability and enhances the attractiveness of its offline store strategy. Moreover, this suggests that Lianjia's market entry and subsequent strategies are more immediately impactful in less mature markets.

@@

In the preceding section, our research has been directed toward evaluating the dynamic effect of Lianjia's offline stores operation. However, there is an imperative to conduct a more detailed analysis of the impact of Lianjia's entry on regional transaction properties. The core of this necessary analysis derives from the premise that the entry of a Lianjia represents an exogenous shock within the respective local segmented market, thus providing a unique opportunity to study the effect of offline expansion on local real estate market. To facilitate such an analysis, we have constructed a series of dummy variables associated with the presence of the Lianjia within the marketplace, delineated as $pre_2$, $pre_1$ (before entry), $entry$, $post_1$, $post_2$, and $post_3$ (successive post-entry intervals), which encapsulate the respective temporal epochs relative to the Lianjia's entry. To eliminate the effect of the well constructed effect, we drop all the variables that have Lianjia's offline stores before the year 2016 to better estimate the effect of Lianjia's entry on the market. These binary indicators serve as central regressors within a structured econometric model with $pre_1$ as the control group, described in Equation \eqref{eq:entry_effect}:

@@

In the post-entry periods ($post_1$, $post_2$, and $post_3$), the results exhibit notable variations. The first period after entry ($post_1$) shows no significant changes in any of the metrics analyzed. However, in the subsequent post-entry periods ($post_2$ and $post_3$), there are significant negative effects on both revenue and the number of house tours. These declines suggest a deterioration in Lianjia's performance and customer engagement, likely attributable to the impact of the epidemic, which led to a decrease in overall revenue. Interestingly, Lianjia's entry does not have a significant effect on price concessions but does show a negative impact on the number of house tours during the epidemic periods. This negative effect is also attributed to the epidemic, which reduced the frequency of house tours due to heightened health concerns and mobility restrictions.

@@

To verify the robustness of the entry effect, we classified the sample into low and high Herfindahl-Hirschman Index (HHI) groups. The results, presented in Table \ref{tab:entry_effect_robustness}, indicate that the entry effect is more pronounced in the high HHI group, with an impact of 6.8\%, and this effect persists into the subsequent period, increasing to 7.8\%. However, following the epidemic, the effect becomes significantly negative in the low HHI group, suggesting that the entry effect is more adversely affected by epidemic policies in less concentrated markets. Conversely, the effect remains non-significant in the high HHI group. Additionally, Lianjia's entry does not significantly influence price concessions in either group, nor does it significantly affect the number of house tours. However, post-epidemic, the number of house tours shows a significantly negative effect in the low HHI group, indicating a more substantial decline in customer engagement in less concentrated markets.

@@

We treat the year 2016 as the base year, and other settings are consistent with previous table \ref{tab:Dynamic}. The result is reported in Figure \ref{fig:dynamic_effect}.

@@

To check the robustness of the result, we also calculated the average number of watching times in the beke's website during the sample periods and estimated the model separately (need to further refine and reformulate).

@@

\clearpage
